%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Summary}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}

%---------------------------------------------------------
 My love to understand things in deeper levels always ended up the same way, tearing down things. Initially I struggled to fix it back. Like any engineer, my life also started with reverse-engineering. Physics classes and Internet Evolved me, fixing things back became easier. I started to modify things ranging from toys to Motorcycles. Things around me evolved, I started learning , I started iterating , building.I started exploring new things to do.
The passion for going Fast got me to Motorcycles.I started modifying my 2-stroke bike for better performance and reliability.I wanted to push the limits. The first electric bike i rode was a huge revelation for me. I was pretty clear electric mobility was the next big thing afterthe 100 year old IC-engines(IC-engines are awesome , no comments).The Volvo city safe car I drove also made me think a lot.
This all was before my Bachelor's degree.Engineering as a professional course helped me to get my roots deeper.
After that i had clear idea to make all my moves carefully ranging from Final year projects to Internship at Keltron to International Internship at Germany funded by DAAD. My first Job is also related to this, India's First Swappable Battery and the SWAP and Charge Station.I'm Still Learning.
Always interested in Electric-vehicle , 2-strokes , Autonomous cars and safety Systems , quadcopters and all things Hardware.



\end{cvparagraph}
